Human capital drives natural selection in contemporary humans

### 2021-04-15 model-appendix.Rmd
Describe how money costs can generate our changing signs for early/late first births. Add Julia code to compute equilibrium with money cost (and for CARA; not used now).

changes with respect to other parameters. We focus on the case $\sigma<1$,
since it gives the closest match to our observations, and since it
also generates ``reasonable'' predictions in other areas, e.g. that
education levels increase with human capital. Figure \ref{fig:theory}
shows how $N^{*}$ changes with $h$ for $a=0.4,b=0.25,\sigma=0.7$.

@@

>>>>

changes with respect to other parameters. We focus on the case $\sigma<1$,
since it gives the closest match to our observations, and since it
also generates "reasonable" predictions in other areas, e.g. that
education levels increase with human capital. Figure \ref{fig:theory}
shows how $N^{*}$ changes with $h$ for $a=0.4,b=0.25,\sigma=0.7$.

@@

\subsection*{Including a money cost}

The model can be extended by adding a money cost $m$ per child. Utility is
then

\[
U = u(1 - s - bN_1 - mN_1) + u(w(s,h)(1 - bN_2) - mN_2) + a(N_1 + N_2)
\]

Figure \ref{fig:N-plot-with-m} shows a computed example with 
$a = 0.4, b = 0.175, \sigma = 0.7, m = 0.075$. Fertility first declines steeply with
human capital, then rises. In addition, for parents with low AFLB ($N_1 > 0$), the
fertility-human capital relationship is negative, while for parents with 
higher AFLB ($N_1 = 0$) it is positive.

\begin{figure}
\begin{centering}
\includegraphics[width=9cm, height=6cm]{N-plot-with-m}
\par\end{centering}
\caption{\label{fig:N-plot-with-m}Fertility vs. human capital in the two-period model
with money costs of children. $a=0.4,b=0.175,\sigma=0.7, m = 0.075$.}
\end{figure}

### 2021-04-15 why-natural-selection.Rmd
Describe how money costs can generate our changing signs for early/late first births. Add Julia code to compute equilibrium with money cost (and for CARA; not used now).

Our results are actually stronger than this, in that correlations with
fertility are reversed at higher AFLB. This could occur if relative risk 
aversion increased at higher income levels.

>>>>

Our results are actually stronger than this, in that correlations with
fertility are reversed at higher AFLB. This could be accommodated in the model 
if children have a money cost as well as a time cost, since money costs are less
burdensome at higher wages, i.e. in period 2 for those with high human capital. Appendix Figure \@ref(fig:N-plot-with-m) shows an example.
